Causal Bandits: Learning Good Interventions via Causal Inference

### 2016-05-19 causal-bandit/nips_2016/introduction.tex
updates related work section

\paragraph{Related Work} As alluded to above, causal bandit problems with $N$ possible interventions can be treated as a classical $N$-armed bandit problem by simply ignoring the causal model and extra observations that are revealed each round. In the farming example, the farmer could treat the six possible interventions as arms, ignore the observations of the non-intervened variables and apply an existing best-arm identificaion algorithm with well understood simple regret guarantees \citep{Jamieson2013}. However, as we show in \S\ref{sec:simple-regret}, this approach ignores the extra information available in the non-intervened variables and subsequently yields sub-optimal performance.

@@

There have been several proposals for bandit problems where extra feedback is received after an action is taken.
Most recently, \citet{Alon2015}, \citet{Kocak2014} have considered very general models related to partial monitoring games~\citep{Bartok2014} where rewards on unplayed actions are revealed according to a feedback graph. As we discuss in \S\ref{sec:discussion}, the problem they consider shares some similarity with ours however their results are for cumulative regret and thus cannot be used to guarantee low simple regret~\citep{Bubeck2009a}. Even without this difference, none
of these algorithms could be applied to our general setting without modification and even in the parallel bandit setting their regret guarantees would not be optimal.
The partial monitoring approach taken by \cite{wu2015online}
could be applied in principle (up to modifications for the simple regret) to the parallel bandit, but the resulting strategy would need to know the likelihood 
of each factor in advance, while our strategy learns this online.
\citet{Yu2009} consider bandit problems where a learner chooses an arm to play as well as set of arms to observe rewards for in a stochastic setting where the reward distributions can change infrequently and the aim is to minimize cumulative regret.
They use extra observations to detect changes whereas we assume fixed reward distributions and use extra observations to improve arm selection. 
\citet{Avner2012} analyse bandit problems where the choice of arm to pull and arm to receive feedback on are decoupled. 
The main difference from our present work is our focus on simple regret and exploitation of the more complex information related rewards via the causal graph.
To the best of our knowledge, our paper is the first to analyse simple regret in bandit problems with extra post-action feedback.

% Partial monitoring is a very general framework for for decoupling the feedback from the action and reward. It can be used to classify problems into one of four categories, trivial with no regret, easy with $R_T = \bigthetatilde{\sqrt{T}}$ , hard with $R_T = \bigtheta{T^{2/3}}$ and hopeless with $R_T = \bigomega{T}$ \cite{Bartok2014}. Partial monitoring algorithms yield results that are optimal with respect the horizon $T$ but not other parameters, such as $K$, which is the key focus of incorporating causal structure.

>>>>

\paragraph{Related Work} As alluded to above, causal bandit problems can be treated as classical multi-armed bandit problems by simply ignoring the causal model and extra observations and applying an existing best-arm identification algorithm with well understood simple regret guarantees \citep{Jamieson2013}. However, as we show in \S\ref{sec:simple-regret}, ignoring the extra information available in the non-intervened variables yields sub-optimal performance.

@@

There have been several proposals for bandit problems where extra feedback is received after an action is taken.
Most recently, \citet{Alon2015}, \citet{Kocak2014} have considered very general models related to partial monitoring games~\citep{Bartok2014} where rewards on unplayed actions are revealed according to a feedback graph. As we discuss in \S\ref{sec:discussion}, the parallel bandit problem can be captured in this framework, however the regret bounds are not optimal in our setting. They also focus on cumulative regret, which cannot be used to guarantee low simple regret~\citep{Bubeck2009a}. The partial monitoring approach taken by \cite{wu2015online} could be applied (up to modifications for the simple regret) to the parallel bandit, but the resulting strategy would need to know the likelihood of each factor in advance, while our strategy learns this online. \citet{Yu2009} utilize extra observations to detect changes in the reward distribution, whereas we assume fixed reward distributions and use extra observations to improve arm selection. \citet{Avner2012} analyse bandit problems where the choice of arm to pull and arm to receive feedback on are decoupled. The main difference from our present work is our focus on simple regret and the more complex information linking rewards for different arms via causal graphs. To the best of our knowledge, our paper is the first to analyse simple regret in bandit problems with extra post-action feedback.

%\citet{Yu2009} consider bandit problems where a learner chooses an arm to play as well as set of arms to observe rewards for in a stochastic setting where the reward distributions can change infrequently and the aim is to minimize cumulative regret. They use extra observations to detect changes whereas we assume fixed reward distributions and use extra observations to improve arm selection.
% Partial monitoring is a very general framework for for decoupling the feedback from the action and reward. It can be used to classify problems into one of four categories, trivial with no regret, easy with $R_T = \bigthetatilde{\sqrt{T}}$ , hard with $R_T = \bigtheta{T^{2/3}}$ and hopeless with $R_T = \bigomega{T}$ \cite{Bartok2014}. Partial monitoring algorithms yield results that are optimal with respect the horizon $T$ but not other parameters, such as $K$, which is the key focus of incorporating causal structure.
